Page not found

### 2023-06-19 manuscript/chapters/3_mappings.qmd
continuity

### Mappings of $[0,1]$ into $[0,1]^2$

TOOD : merge with previous

Since in the composition $w_U \circ S^{-1}$ we work with the inverse mapping, we contextualize our study by first considering the types of functions from $[0,1]$ into $[0,1]^2$. We have already established that there is no homeomorphism between those spaces, and need to relax one of the conditions. Since bijections are functions that are both injective and surjective, we can represent Netto's theorem as a 3-way Venn diagram in @fig-venn.

@@

The 3-way intersection of the Venn diagram represents that functions which are both bijective (surjective and injective) and continuous do not exist.

For the three remaining 2-way intersections, we cite, without going into detail, the types of functions which they represent (see [@kharazishvili_strange_2017] for Cantor and Peano functions, [@sagan_space-filling_1994] for Peano and Jordan functions):

* Cantor functions are bijections $[0,1] \mapsto [0,1]^2$. However, they are not continuous, and thereby break the continuity of the kernel.
* Jordan curves are continuous injections $[0,1] \mapsto [0,1]^2$. Since they are not surjective, these curves cannot entirely "fill" the $[0,1]^2$ space, and we will not use them.
<!-- Nicole : see my notebook about Jordan functions and their nonzero Jordan measure -->
* Peano curves are continuous surjections $[0,1] \mapsto [0,1]^2$. Their non-injectivity however is not a problem, since it just means that two segment populations can "refer" to the same square population (see @fig-non-injection). Therefore, Peano functions seem like good candidates for the mapping $S^{-1}$.

>>>>

@fig-venn shows a visual representation of Netto's theorem. The 3-way intersection of the Venn diagram represents that functions which are both bijective (surjective and injective) and continuous do not exist. For the three remaining 2-way intersections, we annotate, without going into detail, the types of functions which they represent (see [@kharazishvili_strange_2017] for Cantor and Peano functions, [@sagan_space-filling_1994] for Peano and Jordan functions).

<!-- ### Mappings of $[0,1]$ into $[0,1]^2$

Since in the composition $w_U \circ S^{-1}$ we work with the inverse mapping, we contextualize our study by first considering the types of functions from $[0,1]$ into $[0,1]^2$. We have already established that there is no homeomorphism between those spaces, and need to relax one of the conditions. Since bijections are functions that are both injective and surjective, we can represent Netto's theorem as a 3-way Venn diagram in @fig-venn. -->

@@

<!--
* Cantor functions are bijections $[0,1] \mapsto [0,1]^2$. However, they are not continuous, and thereby break the continuity of the kernel.
<!-- Nicole: ACTUALLY NO THIS IS NOT A PROBLEM !! OUR Z-MAPPING IS NOT CONTINUOUS, BUT LOCALITY STILL SAVES US, SO THAT IT IS CONTINUOUS "ON AVERAGE"
* Jordan curves are continuous injections $[0,1] \mapsto [0,1]^2$. Since they are not surjective, these curves cannot entirely "fill" the $[0,1]^2$ space, and we will not use them.
<!-- Nicole : see my notebook about Jordan functions and their nonzero Jordan measure
* Peano curves are continuous surjections $[0,1] \mapsto [0,1]^2$. Their non-injectivity however is not a problem, since it just means that two segment populations can "refer" to the same square population (see @fig-non-injection). Therefore, Peano functions seem like good candidates for the mapping $S^{-1}$.
-->

### 2023-06-19 manuscript/chapters/4_locality.qmd
continuity

The definition of locality can essentially be seen as a weakened version of continuity; since from definition the image of a small neighbourhood through a continuous function is also a small neighbourhood. Therefore, continuity of a function $f$ implies that $V_n(f) \xrightarrow{n \to \infty} 0$. The reverse is obviously not true, since for instance the metric $V_n$ vanishes when applied to a step function, which is only piecewise continuous.

>>>>

The definition of locality can essentially be seen as a weakened version of continuity, or "continuity on average". A continuous function $f$ evidently verifies $V_n(f) \xrightarrow{n \to \infty} 0$, since small neighbourhoods are mapped to small neighbourhoods. The reverse is obviously not true, since for instance the metric $V_n$ vanishes when applied to a step function, which is only piecewise continuous.
